---
title: "Final"
output: html_document
---

This is for the final project of practical machine learning coursera.

The training data: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv


Reference:

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

The paper claimed to use random forest, 10-cross-validation with bagging.

First load libraries:
```{r}
library(ggplot2)
library(reshape2)
library(AppliedPredictiveModeling)
library(caret)
setwd("/Users/xiem1/Desktop/class/practical_machine_learning/")
```

Read in training data:
```{r}
trainingData<-read.csv("pml-training.csv",header = TRUE)
## get the traning data with label
trainingWLE<-trainingData[,setdiff(c(grep('accel',names(trainingData)),ncol(trainingData)),grep('var_',names(trainingData)))]

### OK, testing here
testingData<-read.csv("pml-testing.csv",header = TRUE)
testingWLE<-testingData[,setdiff(c(grep('accel',names(testingData)),ncol(testingData)),grep('var_',names(testingData)))]


```

Let's see how data distributed

```{r}
trainingWLE_data<-subset(trainingWLE,select = -classe)
summary(trainingWLE_data)
```

To see correlation between features:

```{r, echo=FALSE}
qplot(x=Var1, y=Var2, data=melt(cor(trainingWLE_data, use="p")), fill=value, geom="tile") +
  scale_fill_gradient2(limits=c(-1, 1))
```

Conclude: there is no outstanding correlation between features.

I will use 10 cross validation which is popular for this kind of research.

```{r}
set.seed(222)
fitControl <- trainControl(method = "cv",number = 10)
mod<-train(classe~. , method="rf",data=trainingWLE,trControl = fitControl)
mod
pred<-predict(mod,testingWLE)
```

My estimation is that my model accuracy will be 95.5% using mtry=2 with SD 4.59e-3.

now here is my prediction

```{r}
pred<-predict(mod,testingWLE)
finalResult<-data.frame(pred,testingWLE[,"problem_id"])
finalResult
```

